Type Refinements for the Working Class

### 2015-11-12 paper.tex
reword sentence about functionality

Martin-L\"of's key innovation was the commitment to pervasive functionality
(extensionality) as part of the \emph{definitions} of the judgments and the
types, in contrast to the state of affairs in formal type theory where
functionality is a metatheorem which may or may not hold depending on the
particular equational theory which has been imposed. Furthermore, models for
behavioral type theory interpret the types as partial equivalence relations on
only closed terms, and the meaning of the hypothetical judgment is defined
separately and uniformly in the logical relations style.

>>>>

Martin-L\"of's key innovation was the commitment to pervasive functionality
(extensionality) as part of the \emph{definitions} of the judgments and the
types, in contrast to the state of affairs in formal type theory where
functionality is a metatheorem which must be shown to obtain, based on the
(somewhat arbitrary) equational theory which has been imposed. Furthermore,
models for behavioral type theory interpret the types as partial equivalence
relations on only closed terms, and the meaning of the hypothetical judgment is
defined separately and uniformly in the logical relations style.
